The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-16 paper.tex
update

 The most interesting finding is that there is a innermost bubbles\
 (dashed box in top left panel of \Cref{fig__jetI5+ismSeed3-45deg})\
 also extending out from the Galactic center on either side of the thin disk.\
 The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$ -- $10^{-2}$ cm$^{-3}$),\
 and underpressured with respect to the turbulent plasma.\
 Moreover, the close-up view of profiles around $z=3.7$ kpc (right column of \Cref{fig__profile})
 demonstrates that there is a sharp pressure jump and dense shell at $z=3.61$ kpc
 indicating that the innermost bubbles are an expanding reverse shock.

 Comparison between the clumpy (first column from left)\
 and the smooth disc (second) in a stratified atmosphere\
 shows that the initial density distribution of the dense disc has an insignificant effect\
 on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
 in an uniform atmosphere (third) is spherical-shape,\
 suggesting the stratification facilitates the outermost bubbles elongation significantly.\
 Also, the two rightmost columns reveal that the development of the innermost bubbles (dashed box)\
 is always associated with the disc, and without the disc,\
 the outermost bubbles and the turbulent region will be oblique,\
 indicating the dense disc is crucial for\
 the symmetry of the Galactic bubbles and for the innermost bubbles formation.

>>>>

 The most interesting finding is that there is a innermost bubbles\
 (dashed box in top left panel of \Cref{fig__jetI5+ismSeed3-45deg})\
 extending out from the Galactic center on either side of the thin disk.\
 The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$ -- $10^{-2}$ cm$^{-3}$),\
 and underpressured with respect to the turbulent plasma.\
 Moreover, the close-up view of profiles around $z=3.7$ kpc (right column of \Cref{fig__profile})
 demonstrates that there is a sharp pressure jump and dense shell at $z=3.61$ kpc,\
 indicating that the innermost bubbles are an expanding reverse shock.\
 We also find that the turbulent plasma is bracketed between the downstream of reverse shock\
 and of the outermost forward shock, thus heating the turbulent plasma up considerably.

 We stressed that either the outermost, turbulent plasma, or innermost bubbles\
 are symmetric about the Galactic plane despite the jet is tilted to the disk normal\
 at an angle $45^{\circ}$.

 To explore how the disk affect the formation of the Galactic bubbles,\
 we compare the fiducial run (first column from left)\
 with the case with the smooth disc (second) in a stratified atmosphere.\
 The results show that the initial density distribution of the dense disc has an insignificant effect\
 on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
 in an uniform atmosphere (third) is spherical-shape,\
 suggesting the stratification facilitates the outermost bubbles elongation significantly.\
 Also, the two rightmost columns reveal that the development of the innermost bubbles (dashed box)\
 is always associated with the disc, and without the disc,\
 the outermost bubbles and the turbulent region will be oblique,\
 indicating the dense disc is crucial for\
 the symmetry of the Galactic bubbles and for the innermost bubbles formation.
